---
title: "R Notebook"
output: pdf_document
---

#loading library
```{r}
library(tidyverse)
```

#loading dataset
```{r}
loan_approval <- read.csv("C:/Users/santo/OneDrive/Desktop/Fundamental of machinelearning/Assignment_1/loan_approval_dataset.csv")
head(loan_approval)
```
#Explanation
#This code reads a CSV file containing loan approval data into an R data frame named "loan_approval" and then displays the first few rows of the dataset for a quick overview of the data.
```{r}
quantitative_vars <- c("loan_amount", "loan_term", "cibil_score")
quantitative_stats <- summary(loan_approval[, quantitative_vars])
print("Descriptive Statistics for Quantitative Variables:")
print(quantitative_stats)
```
#Explanation
#This code provides descriptive statistics (summary statistics) for specific quantitative variables in the "loan_approval" data frame and quantitative variables in the dataset.
```{r}
categorical_var <- c("education","self_employed", "loan_status")
categorical_summary <- table(loan_approval[, categorical_var])
print("Summary for Categorical Variable:")
print(categorical_summary)
```
#Explanation
#This code provides categorical statistics (summary statistics) for specific categorical variables in the "loan_approval" data frame and categorical variables in the dataset.
```{r}
#Transform the "loan_amount" variable by adding a constant value
constant_value <- 1000000
loan_amount_transformed <- loan_approval$loan_amount + constant_value
#Display the first few rows of the dataset after transformation
print("Dataset after transforming 'loan_amount':")
print(head(loan_amount_transformed))
```
#Explanation
#This code shows how to transform a variable in a dataset by adding a constant value. It adds 1,000,000 to each observation in the "loan_amount" variable and displays the first few rows of the dataset after this transformation.
```{r}
# Plot histogram for the distribution of "income_annum"
hist(loan_approval$no_of_dependents)
```
#Explanation
#The resulting plot will show the distribution of the "no_of_dependents" variable, giving insights into the number of dependents for individuals in the dataset. Histograms are useful for visualizing the shape and spread of a distribution and identifying patterns in the data.
```{r}
# Plot scatterplot between "income_annum" and "loan_amount"
plot(loan_approval$income_annum,loan_approval$loan_amount)
```
#Explanation
#The graph shows the relationship between "income_annum" and "loan_amount" in the "loan_approval" dataset. x-coordinate corresponding to the "income_annum" value and the y-coordinate corresponding to the "loan_amount" value.This type of plot is useful for identifying patterns or trends between two numeric variables.



